---
name: Benjamin
surname: Elsner
address: "University College Dublin, School of Economics, Belfield, Dublin 4, Ireland"
phone: +353 1 716 8446
www: benjaminelsner.com
email: "benjamin.elsner@ucd.ie"
twitter: ben_elsner
github: benelsner82
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(scholar)

scholarben <- get_profile("jvyIv10AAAAJ")
```



# Research Interests

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.


# Current Positions

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where,
  "Assistant Professor (with tenure)", "2018", "University College Dublin", "Dublin, Ireland",
  "Research Fellow", "2018-", "Institute of Labor Economics (IZA)", "Bonn, Germany",
  "Research Fellow", "2016-", "Centre for Research and Analysis of Migration (CReAM), University College London", "London, UK",
  "Research Fellow", "2018-", "Geary Institute for Public Policy", "Dublin, Ireland",  
) %>% 
  detailed_entries(Position, Year, Institution, Where)
```

# Past Positions

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD Economics", "2013", "Trinity College Dublin", "Dublin, Ireland",
  "M.A. Economics", "2008", "Universität Regensburg", "Regensburg, Germany",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```




# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

**Number of citations**: `r scholarben$total_cites`; **h-index**: `r scholarben$h_index`

## Refereed Journals



```{r}
knitr::write_bib(c("izawol22",
                   "itax18",
                   "obes18",
                   "jhr18",
                   "jole17",
                   "jie13", 
                   "jpopecon13"), 
                 "publications.bib")

bibliography_entries("publications.bib") %>%
  arrange(desc(issued$year))

```

## Edited Book

```{r}
knitr::write_bib(c("borjas18"), 
                 "books.bib")

bibliography_entries("books.bib") %>%
  arrange(desc(issued$year))

```

## Book Chapters and Policy Reports

```{r}
knitr::write_bib(c("worldscientific"), 
                 "chapters.bib")

bibliography_entries("chapters.bib") %>%
  arrange(desc(issued$year))

```


# Working Papers 

```{r}
knitr::write_bib(c("biavaschi13", "bellani22", "chevalier23"), 
                 "workingpapers.bib")

bibliography_entries("workingpapers.bib") %>%
  arrange(desc(issued$year))

```



# Work in Progress 


- The Impact of Brexit on Irish Firms and Workers (joint with Eoin Flaherty and Stefanie Haller)
- Gender Norms and Time Use: Pan-European Evidence from School Closures during Covid-19 (joint with Manvi Jindal, Massimiliano Mascherini and Sanna Nivakoski)



# Grants

```{r}
library(tibble)
tribble(
  ~ Funder, ~ Year, ~ Details, ~ Sum,
  "Irish Research Council", "2021", "Government of Ireland Postgraduate Scholarship", "Co-PI with Michele Gubello, 55,000€",  
  "World Bank, UK Aid and UNHCR", "2020", "Forced Migration, Social Cohesion and Conflict", "PI, 25,000USD",  
  "Irish Research Council", "2020", "Government of Ireland Postgraduate Scholarship", "Co-PI with Diego Zambiasi, 48,000€",  
  "Irish Research Council", "2019", "Government of Ireland Postgraduate Scholarship", "Co-PI with Emanuele Albarosa, 72,000€",
  "German Ministry of Education (BMBF)", "2017", "Determinants of College Dropout (with Ingo E. Isphording, Florian Wozny and Ulf Zölitz)", "170,000€",
  "Irish Research Council (IRCHSS)", "2011", "Government of Ireland Postgraduate Scholarship", "PI, 16,000€",
  "Strategic Innovation Fund", "2008", "PhD Scholarship", "PI, 48,000€",  
  "Haniel Foundation", "2005", "Go East Scholarship for Studies Abroad", "PI, 3,000€",  
) %>% 
  detailed_entries(Funder, Year, Details, Sum)
```


# Honors and Awards

```{r}
library(tibble)
tribble(
  ~ Award, ~ Year, ~ Details,
  "Teaching Excellence Award", "2022", "UCD College of Social Sciences and Law",
  "Best Paper Award", "2018", "Spring Meetings of Young Economists",  
  "Novartis Prize", "2018", "Best Paper in Health Economics, Irish Economic Association", 
  "Best Paper Prize", "2016", "Warsaw International Economic Meeting",  
  "Excellence in Refereeing Award", "2015", "Labour Economics",
  "FEEM Award", "2010", "Best Paper Presented by a Young Economist at the EEA Conference",
  "Christa Lindner Preis", "2008", "Best M.A. Thesis at the University of Regensburg",
) %>% 
  detailed_entries(Award, Year, Details)
```


# Invited Seminars

## 2023
University of Surrey, University of Padova, IRVAPP-FBK (Trento), University of Bolzano

## 2022
UCD Geary Institute, KU Leuven (LICOS), University of Strathclyde

## 2021
University of Innsbruck, KU Ingolstadt-Eichstätt

## 2020
University of Groningen, Graduate Institute (Geneva), University of St. Andrews, University of Cardiff

## 2019
Universit\`{a} degli Studi di Milano-Bicocca, Queen's University Belfast, ESRI, VU Amsterdam, University of Vilnius, University of Potsdam

## 2018
UCD Geary Institute, Trinity College Dublin, CERGE-EI Prague, Masaryk University Brno, Paris School of Economics, University of Trier, LISER (Luxembourg)

## 2017
University College Dublin, Paris School of Economics, OECD, University of Freiburg, RWI Essen, IOS Regensburg, University of Regensburg

## 2016 
SOFI Stockholm, Maastricht University, University of Cologne,  University of Colorado Denver, University of Leicester, University of Oxford, University of Duisburg-Essen, University of Kent, University of Bayreuth, University of Bonn

## 2015
University of Mainz, IAB Nuremberg, Modul University Vienna, WU Vienna, Concordia University, University of Mannheim, University of Regensburg, HHU Dusseldorf

## 2014
DIAL (Paris), NIW (Hannover), University of Hamburg, Temple University, George Washington University, HHU Dusseldorf, University of Heidelberg, University of Freiburg, IRES-UC Louvain

## 2013
University College Dublin, University of Southern Denmark, IOS Regensburg, University of Münster

## 2012
University of Edinburgh, LMU Munich, IZA Bonn, University of Stirling

## 2011
UCD Geary Institute, NUI Maynooth, SSE Riga, Bocconi University, Fondazione Eni Enrico Mattei (Milan), Institute for East European Studies (Regensburg)

## 2010
Trinity College Dublin


# Conference Presentations



# Supervision

## PhD Students 

Emanuele Albarosa (UCD, 2018-2022; first placement: Economist, IOM/United Nations) 

Diego Zambiasi (UCD, 2018-2022, first placement: Lecturer with tenure, Newcastle University) 

Stefano Ceolotto (TCD, co-advisor, 2019-2022, first placement: Post-Doc, ESRI) 

Mohsin Javed (UCD, 2019-) 

Michele Gubello (UCD, 2019-, first placement: Post-Doc, ESRI) 

Dimitrios Argyros (UCD, 2021-) 

Manvi Jindal (UCD, 2021-) 

Aditi Kharb (UCD, 2022-) 


## Post-Doc 
Nicolas Apfel (letter writer 2020-2022; PhD at U Regensburg; first placement: Post-Doc at U Surrey; currently permanent Lecturer at U Southampton)

## M.Sc Students (first placement in brackets)
Christoph Deuster (U Bonn, 2013; PhD student UC Louvain), Anusha De (UCD, 2019; PhD student KU Leuven), Rafan Alfrayyan (UCD, 2019, Economist at Saudi Ministry of Finance), Jeff Concannon (UCD, 2021; Analyst at Frontier Economics), Wendy Disch (UCD, 2021; Researcher at ESRI), Stephen Fowler (UCD, 2021; MPP Harris School, U Chicago), Anthony Jordan (UCD, 2021, Irish Government Economic and Evaluation Service), Cormac Harten (UCD, 2022, Analyst at Glenveagh Properties), Cecilie Gjendem (UCD, 2022, Analyst at LinkedIn), Ian Moran (UCD, 2023) 



# Reviewing

## Refereed Journals (87 Articles)

American Economic Review (2x), American Economic Review: Insights, Review of Economic Studies (2x), Journal of Human Resources (6x), Journal of International Economics (2x), Journal of Labor Economics (4x), Journal of Public Economics (2x), Journal of the European
Economic Association (3x), Management Science, Review of Economics \& Statistics (3x), Canadian Journal of Economics, European Economic Review (2x), Industrial and Labor Relations Review, Journal of Applied Econometrics, Journal of Econometrics, Journal of
Economic Behavior and Organization (3x), Journal of Economic Dynamics and
Control,  Journal of Economic Geography, Journal of Population Economics (3x), Journal of the Association of Environmental and Resource Economists, Journal of Urban Economics (2x), Labour Economics (3x),
Regional Science and Urban Economics (3x), Scandinavian Journal of Economics, American Journal of Health Economics, Economics of Education Review (4x), Economic Policy, Health Economics,
Journal of Regional Science, Review of Development Economics, Review of
Income and Wealth, Review of International Economics, China Economic Review, Economic Systems, Empirical Economics (2x), Fiscal Studies, German Economic
Review (3x), International Journal of Manpower, International Migration Review, IZA Journal of Development and Migration, IZA Journal of European Labor
Studies, IZA Journal of Labor Economics, IZA Journal of Migration, IZA World
of Labor (3x), Journal of Applied Economics, Journal of Common Market Studies, Journal of Development Studies, Migration Studies, Oxford Development Studies, Review of the World Economy, Scottish Journal of Political Economy, Social Science and Medicine, Socio-Economic Review


## Grant Reviews

GLM-LIC (IZA and DFID, 2x)

OeNB Jubiläumsfonds (Austrian National Bank)

Czech Science Foundation (2x)

Economic and Social Resarch Institute (ESRI; review of policy report)


## Conference Selection Committees

DIAL conference "Barriers to Development" (2015)

Annual Conference of the German Economic Association (Verein für Socialpolitik, 2017, 2020)

Annual Meetings of the European Economic Association (2023)


# Teaching

## Innovations

## Qualification

## Courses


## Guest Lectures and Masterclasses


# Academic Service

## Editorships

## Managerial Roles

## Conference Organization

# Skills

## Software
R, RMarkdown, Stata, LaTeX, HTML

## Languages
German (native), English (fluent), French, Polish (good), Italian, Czech, Russian (some)
