---
name: Benjamin
surname: Elsner
address: "University College Dublin, School of Economics, Belfield, Dublin 4, Ireland"
phone: +353 1 716 8446
www: benjaminelsner.com
email: "benjamin.elsner@ucd.ie"
twitter: ben_elsner
github: benelsner82
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(vitae)
library(dplyr)
library(scholar)

scholarben <- get_profile("jvyIv10AAAAJ")

#scholarben <- as.data.frame(1)
#scholarben$total_cites <- 1
#scholarben$h_index <- 1
```



# Research Interests

My research interests lie at the intersection of labour economics, international economics, and environmental economics. I currently pursue three strands of research: 
\medskip

1. impact of **migration** on the sending and receiving countries,

2. impact of the **environment** (especially pollution) on human capital formation, 

3. the effect of **peers** and teachers on human capital,


# Current Positions

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where,
  "Assistant Professor (with tenure)", "2018-", "University College Dublin", "Dublin, Ireland",
  "Research Fellow", "2018-", "Institute of Labor Economics (IZA)", "Bonn, Germany",
  "Research Fellow", "2016-", "Centre for Research and Analysis of Migration (CReAM), University College London", "London, UK",
  "Research Fellow", "2018-", "Geary Institute for Public Policy", "Dublin, Ireland",  
) %>% 
  detailed_entries(Position, Year, Institution)
```

# Past Positions

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where,
  "Senior Research Associate", "2014-2017", "Institute of Labor Economics (IZA)", "Bonn, Germany",
  "Research Associate", "2012-2014", "Institute of Labor Economics (IZA)", "Bonn, Germany",
) %>% 
  detailed_entries(Position, Year, Institution)
```


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD Economics", "2013", "Trinity College Dublin", "Dublin, Ireland",
  "M.A. Economics", "2008", "Universität Regensburg", "Regensburg, Germany",
) %>% 
  detailed_entries(Degree, Year, Institution)
```



<!--
# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

-->

# Publications

Google scholar: **Number of citations**: `r scholarben$total_cites`; **h-index**: `r scholarben$h_index`

## Refereed Journals



```{r}
knitr::write_bib(c("izawol22",
                   "itax18",
                   "obes18",
                   "jhr18",
                   "jole17",
                   "jie13", 
                   "jpopecon13"), 
                 "publications.bib")

bibliography_entries("publications.bib") %>%
  arrange(desc(issued$year))

```

## Edited Book

```{r}
knitr::write_bib(c("borjas18"), 
                 "books.bib")

bibliography_entries("books.bib") %>%
  arrange(desc(issued$year))

```

## Book Chapters and Policy Reports

```{r}
knitr::write_bib(c("worldscientific"), 
                 "chapters.bib")

bibliography_entries("chapters.bib") %>%
  arrange(desc(issued$year))

```


# Working Papers 

```{r}
knitr::write_bib(c("biavaschi13", "bellani22", "chevalier23"), 
                 "workingpapers.bib")

bibliography_entries("workingpapers.bib") %>%
  arrange(desc(issued$year))

```



# Work in Progress 


1. The Impact of Brexit on Irish Firms and Workers (joint with Eoin Flaherty and Stefanie Haller)
2. Gender Norms and Time Use: Pan-European Evidence from School Closures during Covid-19 (joint with Manvi Jindal, Massimiliano Mascherini and Sanna Nivakoski)
3. Air Pollution and High-Stakes Decision Making (joint with Florian Wozny)



# Grants

```{r}
library(tibble)
tribble(
  ~ Funder, ~ Year, ~ Details, ~ Sum,
  "European Economic Association", "2023", "Seedcorn Grant for the Development of Innovative Teaching", "2,000€",    
  "Irish Research Council", "2023", "Government of Ireland Postgraduate Scholarship", "Co-PI with Dimitrios Argyros, 56,000€",   
  "Irish Research Council", "2021", "Government of Ireland Postgraduate Scholarship", "Co-PI with Michele Gubello, 55,000€",  
  "World Bank, UK Aid and UNHCR", "2020", "Forced Migration, Social Cohesion and Conflict", "PI, 25,000USD",  
  "Irish Research Council", "2020", "Government of Ireland Postgraduate Scholarship", "Co-PI with Diego Zambiasi, 48,000€",  
  "Irish Research Council", "2019", "Government of Ireland Postgraduate Scholarship", "Co-PI with Emanuele Albarosa, 72,000€",
  "German Ministry of Education (BMBF)", "2017", "Determinants of College Dropout (with Ingo E. Isphording, Florian Wozny and Ulf Zölitz)", "170,000€",
  "Irish Research Council (IRCHSS)", "2011", "Government of Ireland Postgraduate Scholarship", "PI, 21,000€",
  "Strategic Innovation Fund", "2008", "PhD Scholarship", "PI, 48,000€",  
  "Haniel Foundation", "2005", "Go East Scholarship for Studies Abroad", "PI, 3,000€",  
) %>% 
  detailed_entries(Funder, Year, Details, Sum)
```


# Honors and Awards

```{r}
library(tibble)
tribble(
  ~ Award, ~ Year, ~ Details,
  "Teaching Excellence Award", "2022", "UCD College of Social Sciences and Law",
  "Best Paper Award", "2018", "Spring Meetings of Young Economists",  
  "Novartis Prize", "2018", "Best Paper in Health Economics, Irish Economic Association", 
  "Best Paper Prize", "2016", "Warsaw International Economic Meeting",  
  "Excellence in Refereeing Award", "2015", "Labour Economics",
  "FEEM Award", "2010", "Best Paper Presented by a Young Economist at the EEA Conference",
  "Christa Lindner Preis", "2008", "Best M.A. Thesis at the University of Regensburg",
) %>% 
  detailed_entries(Award, Year, Details)
```


# Invited Seminars

## 2023
University of Surrey, University of Padova, IRVAPP-FBK (Trento), University of Bolzano, ISEG Lisbon

## 2022
UCD Geary Institute, KU Leuven (LICOS), University of Strathclyde

## 2021
University of Innsbruck, KU Ingolstadt-Eichstätt

## 2020
University of Groningen, Graduate Institute (Geneva), University of St. Andrews, University of Cardiff

## 2019
Università degli Studi di Milano-Bicocca, Queen's University Belfast, ESRI, VU Amsterdam, University of Vilnius, University of Potsdam

## 2018
UCD Geary Institute, Trinity College Dublin, CERGE-EI Prague, Masaryk University Brno, Paris School of Economics, University of Trier, LISER (Luxembourg)

## 2017
University College Dublin, Paris School of Economics, OECD, University of Freiburg, RWI Essen, IOS Regensburg, University of Regensburg

## 2016 
SOFI Stockholm, Maastricht University, University of Cologne,  University of Colorado Denver, University of Leicester, University of Oxford, University of Duisburg-Essen, University of Kent, University of Bayreuth, University of Bonn

## 2015
University of Mainz, IAB Nuremberg, Modul University Vienna, WU Vienna, Concordia University, University of Mannheim, University of Regensburg, HHU Dusseldorf

## 2014
DIAL (Paris), NIW (Hannover), University of Hamburg, Temple University, George Washington University, HHU Dusseldorf, University of Heidelberg, University of Freiburg, IRES-UC Louvain

## 2013
University College Dublin, University of Southern Denmark, IOS Regensburg, University of Münster

## 2012
University of Edinburgh, LMU Munich, IZA Bonn, University of Stirling

## 2011
UCD Geary Institute, NUI Maynooth, SSE Riga, Bocconi University, Fondazione Eni Enrico Mattei (Milan), Institute for East European Studies (Regensburg)

## 2010
Trinity College Dublin


# Conference Presentations


## 2023
EEA-ESEM Annual Meetings (Barcelona)


## 2022
IZA Workshop on Environment, Health and Labor Markets (online), ECA Talks on Forced Migration (World Bank, online)

## 2019
Workshop on Mobility and Migration (Bank of Italy, Rome)


## 2018
Irish Economic Association

## 2017 
IZA Annual Migration Meeting (Bonn), IZA Workshop on the Environment and Labor Markets, EALE (St. Gallen), IZA Workshop on the Economics of Education

## 2016 
SOLE Meetings (Seattle), EALE (Ghent), RGS/RWI Workshop on the Economics of Migration (Essen), IZA Workshop on the Economics of Education, ZEW Workshop on Migration (Mannheim)

## 2015
IZA Workshop "Inequality: Causes and Consequences" (Bonn), SOLE/EALE World Congress (Montreal), Workshop Health.Skills.Education (Essen), IZA/Worldbank Conference on Employment and Development (Bonn), EEA Meeting (Mannheim), Verein für Socialpolitik (M\"{u}nster), Workshop "Immigration in OECD Countries" (Paris)

## 2014

FERDI Workshop "International Labor Mobility and Inequality across Nations" (Clermont-Ferrand), RES Annual Conference (Manchester), SOLE (Arlington, VA), Annual Migration Meeting (Bonn),
EALE (Ljubljana)



## 2013 

RES Annual Conference (RHUL, London), NORFACE migration conference (UCL, London), EALE (Torino), IZA/SOLE Transatlantic Meeting (Munich),
ESPE (Aarhus), Worldbank Migration Conference (Ifrane, Morocco), ETSG (Birmingham), CEMIR workshop on migration (Munich),
IZA/ASE Workshop "EU Enlargement and the Labor Markets" (Bucharest), OECD workshop "Immigration in OECD Countries" (Paris)


## 2012 
RES PhD Meeting (London), Irish Economic Association (Dublin), EEA Meetings (Málaga), ESEM (Málaga), German Economic Association (Göttingen), IZA/CEU Workshop on EU Enlargement and the Labor Markets (Budapest), Immigration in OECD Countries (Paris)

## 2011 
Mainz Workshop in Labor Economics (Mainz), NORFACE Conference "Migration: Economic Change,
Social Challenge" (London), German Economic Association (Frankfurt), Irish Society of
New Economists (Dublin), 2nd TEMPO Conference on International Migration (Vienna), SAE (Málaga)


## 2010
EEA Meetings (Glasgow), Irish Society of New Economists (Dublin), RGS Doctoral Conference (Bochum), Irish Economic Association (Belfast)

## 2009 
Irish Society of New Economists (Limerick)


# Supervision

## PhD Students 

|   Emanuele Albarosa (UCD, 2018-2022; first placement: Economist, IOM/United Nations, Ukraine) 

|   Diego Zambiasi (UCD, 2018-2022, first placement: Lecturer with tenure, Newcastle University) 

|   Stefano Ceolotto (TCD, co-advisor, 2019-2022, first placement: Post-Doc, ESRI; currently at CMCC Venice) 

|   Michele Gubello (UCD, 2019-2023, first placement: Post-Doc, ESRI) 

|   Mohsin Javed (UCD, 2019-) 

|   Dimitrios Argyros (UCD, 2021-) 

|   Manvi Jindal (UCD, 2021-) 

|   Aditi Kharb (UCD, 2022-) 


## Post-Doc 
Nicolas Apfel (letter writer 2020-2022; PhD at U Regensburg; first placement: Post-Doc at U Surrey; currently permanent Lecturer at U Southampton)

## M.Sc Students (first placement in brackets)
Christoph Deuster (U Bonn, 2013; PhD student UC Louvain), Anusha De (UCD, 2019; PhD student KU Leuven), Rafan Alfrayyan (UCD, 2019, Economist at Saudi Ministry of Finance), Jeff Concannon (UCD, 2021; Analyst at Frontier Economics), Wendy Disch (UCD, 2021; Researcher at ESRI), Stephen Fowler (UCD, 2021; MPP Harris School, U Chicago), Anthony Jordan (UCD, 2021, Irish Government Economic and Evaluation Service), Cormac Harten (UCD, 2022, Analyst at Glenveagh Properties), Cecilie Gjendem (UCD, 2022, Analyst at LinkedIn) 

## PhD and Habilitation Examinations 

**External**

|   Stepan Mikula (Masaryk University Brno, examiner on habilitation committee, 2023)

|   Jacopo Bassetto (University of Trento \& University of Bamberg, external PhD examiner, 2022)

|   Vahan Sargsyan (CERGE-EI, external PhD examiner, 2018) 

\medskip

**Internal**

|   Xidong Guo (UCD, PhD committee chair, 2022)

|   Ivan Petrov (UCD, PhD committee chair, 2021)

|   Neil Killeen (UCD, internal PhD examiner, 2018) 


# Reviewing

## Refereed Journals (70 Reports, 48 journals)

American Economic Review (2x), American Economic Review: Insights, Review of Economic Studies (2x), Journal of Human Resources (6x), Journal of International Economics (2x), Journal of Labor Economics (4x), Journal of Public Economics (2x), Journal of the European
Economic Association (3x), Management Science, Review of Economics & Statistics (3x), Canadian Journal of Economics, European Economic Review (2x), Industrial and Labor Relations Review, Journal of Applied Econometrics, Journal of Econometrics, Journal of
Economic Behavior and Organization (3x), Journal of Economic Dynamics and
Control,  Journal of Economic Geography, Journal of Population Economics (3x), Journal of the Association of Environmental and Resource Economists, Journal of Urban Economics (2x), Labour Economics (3x),
Regional Science and Urban Economics (3x), Scandinavian Journal of Economics, American Journal of Health Economics, Economics of Education Review (4x), Economic Policy, Health Economics,
Journal of Regional Science, Review of Development Economics, Review of
Income and Wealth, Review of International Economics, China Economic Review, Economic Systems, Economics Letters, Empirical Economics (2x), Fiscal Studies, German Economic
Review (3x), International Journal of Manpower, International Migration Review, IZA Journal of Development and Migration, IZA Journal of European Labor
Studies, IZA Journal of Labor Economics, IZA Journal of Migration, IZA World
of Labor (3x), Journal of Applied Economics, Journal of Common Market Studies, Journal of Development Studies, Migration Studies, Oxford Development Studies, Review of the World Economy, Scottish Journal of Political Economy, Social Science and Medicine, Socio-Economic Review


## Grant Reviews

|   GLM-LIC (IZA and DFID, 2x)

|   OeNB Jubiläumsfonds (Austrian National Bank)

|   Czech Science Foundation (2x)

|   Economic and Social Resarch Institute (ESRI; review of policy report)


## Conference Selection Committees

|   Annual Meetings of the European Economic Association (2023)

|   Annual Conference of the German Economic Association (Verein für Socialpolitik, 2017, 2020)

|   DIAL conference "Barriers to Development" (2015)






# Teaching


## Programmes Designed

**Structured MLitt/PhD programme in Economics** (UCD, 2018)

- Created the first PhD programme in Ireland with a full first year of coursework
- Tripled enrolment numbers from 17 (2017) to 50 (2020)

\medskip

**M.Sc Economics and Data Analytics** (UCD, 2023)

- Created an M.Sc programme that is jointly offered by the School of Economics and the School of Mathematics and Statistics
- Strong focus on quantitative methods (econometrics, data programming, machine learning)

## Innovations

YouTube Channel with over 70 videos, over 50k views, over 2,300 subscribers

intuitivemetrix.com $\rightarrow$ interactive website for undergraduate econometrics



## Qualification

Professional Certificate in University Teaching \& Learning (University College Dublin, 2019)

## Courses taught

\textbf{University College Dublin}

|   Causal Inference and Policy Evaluation (M.Sc, 2023-)

|   Public Economics (B.Sc, 2019-2022)

|   Econometrics (Ph.D, 2018-)

|   Introduction to Econometrics (B.Sc, 2018-)

|   Economics Research Workshop (B.Sc, 2018-2020)

\medskip

\textbf{European Business School}

|   Introductory Econometrics (PhD, 2014-2020)

|   European Labour Markets (B.Sc, 2014-2017)

\medskip

\textbf{University of Luxembourg}

|   Economics of Migration (PhD, 2017)



\medskip

\textbf{Universität Regensburg}

|   Economics of Migration (B.Sc, M.Sc, 2018)

|   Macroeconomics (B.Sc tutorial, 2006-2007)

|   Microeconomics (B.Sc tutorial, 2008)


\medskip

\textbf{Trinity College Dublin}

|   Microeconomics (M.Sc, tutorial, 2009-2012)


## Guest Lectures and Masterclasses

|   Workshop: R for Practitioners (IGEES, 2023-)

|   Masterclass: New Developments in Causal Inference (Central Bank of Ireland, 2023)

|   Guest lecture: Why International Experience Matters (University of Oldenburg, PhD class, scheduled 2023)

|   Guest lecture: the Welfare Impact of International Migration (University of Groningen, MSc class, scheduled 2023)

|   Masterclass Regression Discontinuity Design (University of Regensburg, MSc class, 2023)

|   Masterclass in Causal Inference (Geary Institute for Public Policy, 2023)

|   Common Pitfalls in Causal Research Designs (Irish Early Career Workshop, TU Dublin, 2023)

|   The 2021 Nobel Prize in Economics (UCD, 2022)

|   Common Pitfalls in Causal Research Designs (Eurofound, Dublin, 2022)

|   Causal Research Designs with DAGs (Örebro University, 2022)

|   Causal Inference for Social Scientists (UCD Social Sciences Summer School, 2021)

|   New Developments in Causal Inference (Central Bank of Ireland, 2019)

|   New Developments in Microeconometrics (Central Bank of Ireland, 2018)

|   The Economics of Brain Drain and Brain Gain (University of Mannheim, 2015)


## Editorships

Research in Labor Economics (Co-Editor, 2022-)

IZA Journal of Labor Economics (Managing Editor, 2013)


## Managerial Roles

**University College Dublin**

|   Programme Director, M.Sc Economics and Data Analytics (2023-)

|   Director of Research and Postgraduate Studies, UCD School of Economics (2022-)

|   Director of the MLitt/PhD Programme in Economics (2018-2021)

|   Member of the Executive Board of the School of Economics (2019-)

\medskip

**Institute of Labor Economics (IZA)**

|   Deputy Director of the Programme Area *Mobility and Migration* (2015-2021)

|   Manager of the guest programme and seminar series (2013-2017)

## Conference Organization


IZA Annual Migration Meeting (co-organizer, Geary Institute, Dublin/Ireland, 2019)

IZA Annual Migration Meeting (co-organizer, Harvard Kennedy School, Cambridge/MA, 2018)

Irish Postgraduate and Early Career Economics Conference (co-organizer, Geary Institute, Dublin/Ireland, 2018)

IZA Annual Migration Meeting (co-organizer, IZA, Bonn/Germany, 2017)

IZA Annual Migration Meeting (sole organizer, IZA, Bonn/Germany, 2016)

IZA Annual Migration Meeting (co-organizer, IZA, Dakar/Senegal, 2015)

Irish Society of New Economists (ISNE, Trinity College Dublin, 2010)


# Skills

## Software
R, RMarkdown, Stata, LaTeX, HTML

## Languages
German (native), English (fluent), French, Polish (good), Italian, Czech, Russian (some)

# References 


\textbf{Prof. Gaia Narciso}, Trinity College Dublin, Department of Economics of Economics. \href{mailto:narcisog@tcd.ie}{narcisog@tcd.ie}

\textbf{Prof. Ron Davies}, University College Dublin, School of Economics. \href{mailto:ronald.davies@ucd.ie}{ronald.davies@ucd.ie}

\textbf{Prof. Paul Devereux}, University College Dublin, School of Economics. \href{mailto:paul.devereux@ucd.ie}{paul.devereux@ucd.ie}

\textbf{Prof. Daniel Hamermesh}, University of Texas at Austin, \href{mailto:hamermes@utexas.edu}{hamermes@utexas.edu}
