---
name: Benjamin
surname: Elsner
address: "University College Dublin, School of Economics, Belfield, Dublin 4, Ireland"
phone: +353 1 716 8446
www: benjaminelsner.com
email: "benjamin.elsner@ucd.ie"
twitter: ben_elsner
github: benelsner82
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(vitae)
library(dplyr)
library(scholar)

scholarben <- get_profile("jvyIv10AAAAJ")

#scholarben <- as.data.frame(1)
#scholarben$total_cites <- 1
#scholarben$h_index <- 1
```



# Research Interests

My research interests lie at the intersection of labour economics, international economics, and environmental economics. I currently pursue three strands of research: 
\medskip

1. impact of **migration** on the sending and receiving countries,

2. impact of the **environment** (especially pollution) on human capital formation, 

3. the effect of **peers** and teachers on human capital,



# Current Positions

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where,
  "Head of School", "2024-", "School of Economics, University College Dublin", "Dublin, Ireland",
  "Professor", "2023-", "University College Dublin", "Dublin, Ireland",
  "Research Fellow", "2018-", "Institute of Labor Economics (IZA)", "Bonn, Germany",
  "Research Fellow", "2016-", "Centre for Research and Analysis of Migration (CReAM), University College London", "London, UK",
  "Research Fellow", "2018-", "Geary Institute for Public Policy", "Dublin, Ireland",  
) %>% 
  detailed_entries(Position, Year, Institution)
```



# Past Positions

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where,
  "Assistant Professor", "2018-2023", "University College Dublin", "Dublin, Ireland",  
  "Senior Research Associate", "2014-2017", "Institute of Labor Economics (IZA)", "Bonn, Germany",
  "Research Associate", "2012-2014", "Institute of Labor Economics (IZA)", "Bonn, Germany",
) %>% 
  detailed_entries(Position, Year, Institution)
```


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD Economics", "2013", "Trinity College Dublin", "Dublin, Ireland",
  "M.A. Economics", "2008", "Universität Regensburg", "Regensburg, Germany",
) %>% 
  detailed_entries(Degree, Year, Institution)
```



# Publications

Google scholar: **Number of citations**: `r scholarben$total_cites`; **h-index**: `r scholarben$h_index`

## Refereed Journals


```{r}
knitr::write_bib(c("jpopecon13"), 
                 "publications1.bib")

bibliography_entries("publications1.bib") %>%
  arrange(desc(issued$year))

```

